---
title: "Lecture10"
author: "Jumpei Fujimoto"
date: "10/2/2019"
output: html_document
---

```{r}
library(ggplot2)
library(socviz)
```

```{r}
head(gss_sm)
```

```{r}
ggplot(gss_sm, aes(x =bigregion)) + geom_bar(aes(y = ..prop.., group=1))
```

```{r}
ggplot(gss_sm, aes(x =region)) +
  geom_bar(aes(y = ..prop.., group=1))+
  coord_flip()

```

```{r}
table(gss_sm$religion)
```
```{r}
ggplot(gss_sm, aes(x =religion)) +
  geom_bar()
```
```{r}
# color blue for graph
ggplot(gss_sm, aes(x =religion)) +
  geom_bar(fill = "blue")
```
```{r}
ggplot(gss_sm, aes(x =religion)) +
  geom_bar(aes(fill = religion))
```
```{r}
ggplot(gss_sm, aes(x =religion, fill = religion)) +
  geom_bar()
```
```{r}
ggplot(gss_sm, aes(x =religion)) +
  geom_bar(aes(fill = religion)) + guides(fill = FALSE)
```
```{r}
ggplot(gss_sm, aes(x =religion)) +
  geom_bar(aes(fill = religion)) + labs(fill="religion")
```
```{r}
ggplot(gss_sm, aes(x =religion, fill = factor(..x..))) +
  geom_bar(aes(y=..prop.., group=1)) + labs(fill="religion") + guides(FALSE)
```
```{r}
ggplot(gss_sm, aes(x =bigregion, fill = religion)) +
  geom_bar()
```
```{r}
ggplot(gss_sm, aes(x =bigregion, fill = religion)) +
  geom_bar(aes(y = ..prop.., group=religion)) 
```

```{r}
# dodge makes side by side
ggplot(gss_sm, aes(x =bigregion, fill = religion)) +
  geom_bar(position = "dodge") 
```
```{r}
# We have to guess what the NA column is
ggplot(gss_sm, aes(x =bigregion, fill = religion)) +
  geom_bar(aes(y = ..prop.., group = religion), position = "dodge") 
```
```{r}
ggplot(gss_sm, aes(x =religion, fill = bigregion)) +
  geom_bar(aes(y = ..prop.., group = bigregion), position = "dodge") +
  facet_wrap(~bigregion)
```

Here are the questions we planned to practice in class today


1. Plot a bar chart by cut for the data set diamonds.


2. Plot a bar chart (proprtions) by cut for the data set diamonds, and give them a gray color.


3. Plot a stacked bar chart for cut by clarity.


4. For each cut, set the bars of the variable clarity side-by-side.


5. Repeat #4 above but change y- axis to show proportions.


6. Facet wrap by clarity
```{r}
?diamonds
head(diamonds)
```
```{r}
ggplot(diamonds, aes(x = cut)) + geom_bar()
```
```{r}
ggplot(diamonds, aes(x = cut)) + geom_bar(aes(y = ..prop.., group=1), fill="gray")
```
```{r}
ggplot(diamonds, aes(x = cut)) +
  geom_bar(aes(y = ..prop.., group=clarity), fill="gray", position = "dodge") 
```
```{r}
ggplot(diamonds, aes(x = cut)) +
  geom_bar(aes(y = ..prop.., group=clarity), fill="gray", position = "dodge") +
  facet_wrap(~clarity)
```



